Visualizing probability distributions across bivariate nonlinear temporal granularities

### 2020-02-14 main.Rmd
text example included (no diagram for periodic and quasi-periodic)

```{r group-periodical, echo=FALSE, out.width = "100%", fig.cap="Linear granularity $B$ groups periodically into linear granularity $G$ with $P = 5$ and $R = 2$, alternating between combining 2 and 3 granules of $B$."}
knitr::include_graphics("Figs/groups_periodically.png")
```

@@

```{r quasi-group-periodical, echo=FALSE, out.width = "100%", fig.cap="Linear granularity $B$ groups quasi-periodically into linear granularity $G$ with $P = 5$ and $R = 2$, alternating between combining 2 and 3 granules of $B$ with $E1$ as the exception."}
knitr::include_graphics("Figs/quasi_groups_periodically.png")
```

**Example**:  Example showing periodic and quasi-periodic linear granularities are displayed in \autoref{fig:group-periodical} and \autoref{fig:quasi-group-periodical} respectively. Each granule is represented by a box. In these figures, the granules that overlap share elements from the underlying time domain. In both of these cases, each granule of $G$ is made up of two and three granules of $B$ alternately. So the period is $P = 5$ and number of granules of $G$ in each period is given by $R=2$. The only difference in \autoref{fig:quasi-group-periodical} is that there is an exception after the first granule of $G$ which consists of one granule of $B$. Except for this exception $E1$, $B$ groups periodically into $G$.

>>>>

<!-- # ```{r group-periodical, echo=FALSE, out.width = "100%", fig.cap="Linear granularity $B$ groups periodically into linear granularity $G$ with $P = 5$ and $R = 2$, alternating between combining 2 and 3 granules of $B$."} -->
<!-- # knitr::include_graphics("Figs/groups_periodically.png") -->
<!-- # ``` -->

@@

<!-- # ```{r quasi-group-periodical, echo=FALSE, out.width = "100%", fig.cap="Linear granularity $B$ groups quasi-periodically into linear granularity $G$ with $P = 5$ and $R = 2$, alternating between combining 2 and 3 granules of $B$ with $E1$ as the exception."} -->
<!-- # knitr::include_graphics("Figs/quasi_groups_periodically.png") -->
<!-- # ``` -->

<!-- **Example**:  Example showing periodic and quasi-periodic linear granularities are displayed in \autoref{fig:group-periodical} and \autoref{fig:quasi-group-periodical} respectively. Each granule is represented by a box. In these figures, the granules that overlap share elements from the underlying time domain. In both of these cases, each granule of $G$ is made up of two and three granules of $B$ alternately. So the period is $P = 5$ and number of granules of $G$ in each period is given by $R=2$. The only difference in \autoref{fig:quasi-group-periodical} is that there is an exception after the first granule of $G$ which consists of one granule of $B$. Except for this exception $E1$, $B$ groups periodically into $G$.  -->

**Example**: Consider the Gregorian calendar without leap year and all their exceptions. Then each month is a grouping of the same number of days over years. So the period is $P = 365$ and number of granules of "months" in each period is given by $R=12$. Thus, we could say days groups periodically into months. Now consider the Gregorian calendar with leap years but none of their exceptions. In such a case, if we consider every February $29^{th}$ as exceptions, we will still have each month as a grouping of the same number of days over years. In that case, we may say days groups quasi-periodically into months. The value of $P$ and $R$ would be 365 and 12 respectively while $E_i$'s would be the time domain corresponding to $29^{th}$ February of any year.
